THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of
free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling, three mixing angles and the CP-violating phase 
of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields. In order to identify which new physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, experiments. This 
approach requires studying each model individually, and calculating every possible observable. There is another approach immitating 
Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual theory and by 
completing it by a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below the mass of the 
new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to the SM
Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-energy 
remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely on the 
symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator coefficients, 
which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model 
predictions if these higher dimensional operators are present in low energy effective SM theory.

>>>>

The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of
free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, three mixing angles and the 
CP-violating phase of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings 
which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond 
the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields. In order to identify which new 
physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, 
experiments. This approach requires studying each model individually, and calculating every possible observable. There is another 
approach immitating Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual 
theory and by completing it by a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
the mass of the new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to 
the SM Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-
energy remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
coefficients,which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the 
standard model predictions if these higher dimensional operators are present in low energy effective SM theory.
